\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
add more to introduction

% call it "Table of Contents" instead of just "Contents"
\addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}

@@

\newpage

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% uncomment this if you want the Table of Contents to have an entry in the
	% table of contents
	% \addcontentsline{toc}{section}{Table of Contents}
	\newpage

	\listoffigures
	% \addcontentsline{toc}{section}{List of Figures}
	\newpage

	\listoftables
	% \addcontentsline{toc}{section}{List of Tables}
	\newpage
\end{singlespace}

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way.

Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example of
this~\autocite{bornoff2000}.

\newpage

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
the most popular apps to use AR, \textit{Pokémon Go}, primarily uses it's AR
feature to place a Pokémon in the world around you through your phone camera for
you to capture. But when it is in the world, it does not interact with anything
around it. It just floats a fixed distance away from you, simply placed on top
of your camera's video feed.

@@

\newpage

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
    \caption{How the Editour looks when a region is being drawn, including the
    two dotted preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

The UI and AR features of the app are very important to the user experience. At
the same time, ARuko is not as purely graphical as it may seem. There is a
significant amount of ``business logic'' that interprets the tour from the
Editour file. On top of this, the geometric checks to test whether the user is
inside a particular arbitrarily-defined geographic region are very important to
get right.  Using Unity's built-in NUnit unit-testing framework, we wrote tests
to verify whether the tour data was being parsed correctly, and whether the tour
would be run correctly.

@@

For this, we implemented a few mathematical functions for individual parts of
the algorithm, such as testing for intersection. We wrote unit-tests to test
each part of the algorithm, so we could be confident that the GPS component of
the app would correctly place users into the correct regions.

@@

\newpage % references should be on their own page

>>>>

% uncomment this to call it "Table of Contents" instead of just "Contents"
% \addto{\captionsamerican}{\renewcommand*{\contentsname}{Table of Contents}}

@@

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% uncomment this if you want the Table of Contents to have an entry in the
	% table of contents
	% \addcontentsline{toc}{section}{Table of Contents}
	\clearpage

	\listoffigures
	% \addcontentsline{toc}{section}{List of Figures}
	\clearpage

	\listoftables
	% \addcontentsline{toc}{section}{List of Tables}
	\clearpage
\end{singlespace}

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
Site~\autocite{unesco} and one of the most popular tourist destinations in
Japan~\autocite{japanguide2019}. However, much of the historic information at
the site is lost on visitors because it is not readily available to non-Japanese
speakers.

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours.

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. This means a few different things. For starters, many AR
apps and features available on smartphones offer very little in the way of
functionality or practicality; quite simply, they are primarily used for minor
spectacles and simple tricks~\autocite{theappsolutions2018}. For example, one of
the most popular apps to use AR, \textit{Pokémon Go}, primarily uses its AR
feature to place a Pokémon in the world around you through your phone camera for
you to capture. But when it is in the world, it does not interact with anything
around it. It just floats a fixed distance away from you, simply placed on top
of your camera's video feed.

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
	\caption{Editour when a region is being drawn, including the two dotted
		preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

The UI and AR features of the app are very important to the user experience. At
the same time, ARuko is not as purely graphical as it may seem. There is a
significant amount of ``business logic'' that interprets the tour from the
Editour file. On top of this, the geometric checks to test whether the user is
inside a particular arbitrarily-defined geographic region are very important to
get right.  Using Unity's built-in NUnit unit testing framework, we wrote tests
to verify whether the tour data was being parsed correctly, and whether the tour
would be run correctly.

@@

For this, we implemented a few mathematical functions for individual parts of
the algorithm, such as testing for intersection. We wrote unit tests to test
each part of the algorithm, so we could be confident that the GPS component of
the app would correctly place users into the correct regions.

@@

\clearpage % references should be on their own page
